% Thank you Josh Davis for this template!
% https://github.com/jdavis/latex-homework-template/blob/master/homework.tex

\documentclass{article}

\newcommand{\hmwkTitle}{Lec\ \#3}

\input{ShortcutsAnalysis}

\begin{document}

\bsc{Theorem 1 (infinum definition)}{

\lt{\es $\neq$ S \sbs \br, S is bounded below.}

Then S possesses a greatest lower bound denoted by \textbf{inf S} (the \textbf{infinum} of S), where inf S \mem \br, satisfying:

\bilist
\item inf S $\leq$ s \fa s \mem S
\item \fa \ep $>$ 0, \exs \uw{s}{1}  st  inf S $+$ \ep $>$ \uw{s}{1}
\elist

\bgpf

\lt{S be bounded below}

Then 

\step{\exs m \mem \br \textrm{  st  }m \leq s \textrm{  }\fa s \mem S}{1}

Define the set -S to be \{$-s$ : s \mem S\}

So, \es $\neq$ -S \sbs \br

From \bpth{1}, -S $\leq$ $-$m \fa s \mem S.

Thus, $-$m is an upper bound for -S.

By the Axiom of Completeness of \br (AoC), sup(-S) \mem \br exists.

By definition,

\step{-s \leq sup(-S), \textrm{  } \fa s \textrm{ } \mem S}{2}

and \fa \ep $>$ 0, \exs \uw{-s}{1} \mem S  st

\step{sup(-S) - \ep < \uw{-s}{1} \textrm{  where  } \uw{s}{1} \mem S}{3}

From \bpth{2}, 

\step{-sup(-S) \leq S \textrm{  } \fa s \mem S}{4}

\wts{$-$sup(-S) \eql inf S}

From \bpth{3},

\step{-sup(-S) + \ep > \uw{s}{1} \textrm{  where  } \uw{s}{1} \mem S }{5}

We see that from \bpth{4} and \bpth{5},

inf S \eql $-$sup(-S).

Hence, result.
\epf

}

\newpage

\bsc{Theorem 3.3.7}{

Given nonempty subsets of A, B (A, B \sbs \br),

\lt{C \eql \{x $+$ y: x \mem A, y \mem B\}}

If A and B have suprema, then C has a supremum: sup C \eql sup A $+$ sup B

\bgpf

\lt{c \mem C}

Then c \eql x $+$ y for some x \mem A, y \mem B.

It follows that:

x $\leq$ sup A, y $\leq$ sup B

x $+$ y $\leq$ sup A $+$ sup B

c $\leq$ sup A $+$ sup B

\step{c \leq sup\textrm{ }A + sup\textrm{ }B \textrm{ } \fa\textrm{ }c \mem C}{1}

By the AoC, sup C \mem \br exists.

For \ep $>$ 0, \exs \uw{x}{0} \mem A, \uw{y}{0} \mem B st

\step{sup \textrm{  } A - \frac{\ep}{2} < \uw{x}{0}}{2}
\step{sup \textrm{  } B - \frac{\ep}{2} < \uw{y}{0}}{3}

From \bpth{2} and \bpth{3}, 

sup A - \frc{\ep}{2} + sup B - \frc{\ep}{2} $<$ \uw{x}{0} $+$ \uw{y}{0} = \uw{c}{0} \mem C

So, 

\step{sup\textrm{ }A + sup\textrm{ }B - \ep < \uw{c}{0}}{4}

From \bpth{1} and \bpth{4}, sup C \eql sup A $+$ sup B

Hence, result.

\epf

}

\newpage

\bsc{Theorem 3.3.8}{

Suppose \es $\neq$ D \sbs \br and 

f : D \lra \br

g : D \lra \br

f(D) \eql \{f(x) : x \mem D\}

If \fa x, y \mem D, f(x) $\leq$ g(y), then
 
f(D) is bounded above and g(D) is bounded below.

Furthermore, sup(f(D)) $\leq$ inf(g(D))

\bgpf

\lt{\uw{y}{0} \mem D}

Then f(x) $\leq$ g(\uw{y}{0}) \fa x \mem D

So, f(D) is bounded above by g(\uw{y}{0}).

By the AoC, sup(f(D)) exists and sup(f(D)) $\leq$ g(\uw{y}{0}) \

\

Since \uw{y}{0} \mem D was arbitrary, we see that

sup(f(D)) $\leq$ g(y) \fa y \mem D

Thus, sup(f(D)) is a lower bound for g(D)

g(D) \eql \{g(y) : y \mem D\}

Hence, inf(g(D)) \mem \br exists and

sup(f(D)) $\leq$ inf(g(D))

Hence, result.

\epf
}

\bsc{Theorem 3.3.9: Archimedian Property / Principle of \br (AP)}{

The set \bn \eql \{1, 2, 3...\} is unbounded above in \br

\bgpf

\supp{\bn is bounded above.}

By the AoC, sup \bn \mem \br exists.

So,

\bilist
\item n $\leq$ sup \bn  \fa n \mem \bn \bpth{1}
\item \fa \ep $>$ 0, \exs n \mem \bn st sup \bn $-$ \ep $<$ \uw{n}{0} \bpth{2}
\elist

Using \bpth{2} with \ep \eql 1, \exs \uw{n}{0}(1) \mem \bn st sup \bn $-$ \ep $<$ \uw{n}{0}

Then, sup \bn $<$ 1 $+$ \uw{n}{0} \bpth{3}

See that \bpth{3} contradicts \bpth{1} with n \eql 1 + \uw{n}{0} \mem \bn

By contradiction, \bn is unbounded.

\epf

}

\end{document}